Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-27 paper/ijcai16.tex
paper: adjust single word in the abstract.

\begin{abstract}
In this paper we propose an approach to preference elicitation that is suitable to large
configuration problem domains where stated preferences can be noisy.
Our setwise max-margin method can be viewed as a generalization of max-margin learning to sets,
and can produce a set of ``diverse'' items that can be used to ask informative queries to the user.
Moreover, the approach can ensuring sparsity in the parameter space, in order to favor the assessment of utility towards combinations of weights that concentrate on just few features.
We present an optimization formulation and show, with simulations, how our approach is able to efficiently elicit the user's utility function even in very large datasets.

>>>>

\begin{abstract}
In this paper we propose an approach to preference elicitation that is suitable to large
configuration problem domains where stated preferences can be noisy.
Our setwise max-margin method can be viewed as a generalization of max-margin learning to sets,
and can produce a set of ``diverse'' items that can be used to ask informative queries to the user.
Moreover, the approach can encourage sparsity in the parameter space, in order to favor the assessment of utility towards combinations of weights that concentrate on just few features.
We present an optimization formulation and show, with simulations, how our approach is able to efficiently elicit the user's utility function even in very large datasets.
